The Weakly Nonlinear Magnetorotational Instability in a thin-gap Taylor Couette flow

### 2016-10-04 paper/thingap_mri_paper.tex
added references; more Vasil discussion; added to abstract; wrote pointless "table of contents"

\title{The Weakly Nonlinear Magnetorotational Instability in a thin-gap Taylor-Couette flow}
\author{Clark, S.E.\altaffilmark{1}}
\author{Oishi, J.S. \altaffilmark{2,}\altaffilmark{3}}

@@

\begin{abstract}
The magnetorotational instability (MRI) is a fundamental process of accretion disk physics, but its saturation mechanism remains poorly understood despite considerable theoretical and computational effort. We present a multiple-scales analysis of the nonideal MRI in the weakly nonlinear regime -- that is, when the the most unstable MRI mode has a growth rate asymptotically approaching zero from above. Here, we develop our theory in a thin-gap, Cartesian channel. Our results confirm Umurhan et al.'s findings that the saturation amplitude follows a Ginzburg-Landau equation. We extend these results by performing a detailed force balance for the saturated $u_y$ and $B_z$ fields, demonstrating that even when diffusive effects are important, the bulk flow saturates by a combination of reducing the background shear and rearranging and strengthening the background $B_z$ field. 
\end{abstract}

@@

For matter to accrete from a disk onto a central object, angular momentum must be transported radially outward in the disk. The transport mechanism is likely turbulent, as molecular viscosity alone cannot account for the needed angular momentum transfer, and likely magnetic, as this turbulence is excited even in hydrodynamically stable disks (\citei{Shakura:1973wg}).  Discovered by \citet{Chandrasekhar:1960wh} and \citet{Velikhov:1959} in global geometry, the MRI was subsequently rediscovered and applied to accretion disks by \citet{Balbus:1991vs}. Since then, the magnetorotational instability (MRI) remains the leading explanation for rapid angular momentum transport in astrophysical disks. The instability in its simplest geometry arises when a differentially rotating disk is threaded by a vertical magnetic field. The presence of the magnetic field linearly destabilizes the disk gas, driving turbulence and angular momentum transport. The MRI likely plays a role in a diverse host of astrophysical systems, including protoplanetary disks and black hole accretion disks, as well as stellar interiors. Despite its importance, many aspects of the MRI remain poorly understood. In particular, the nonlinear saturation mechanism for the MRI is an open question, and a formidable challenge. MRI saturation has been tackled almost exclusively with simulation, with a few notable exceptions detailed below. In this work we investigate the weakly nonlinear behavior of the MRI.

Weakly nonlinear analysis is a perturbative method used to examine the asymptotic behavior of a system near threshold -- that is, when the system is just barely unstable to its most unstable mode. The analytical technique follows the multiscale evolution of fluid variables in a perturbation expansion, allowing the controlled interaction of modes between orders in a perturbation series (see, e.g., Bender \& Orszag for a full mathematical formalism). Weakly nonlinear analysis can be a powerful technique for analytically examining systems which in their full generality exhibit such complicated nonlinear behavior that their study is relegated primarily to the simulation domain. The MRI is one such phenomenon: while there is a rich literature analytically examining the linear MRI, analytical treatments of the \textit{nonlinear} system are relatively few. The weakly nonlinear treatment of the MRI was pioneered by \citeauthor{Umurhan:2007dz} (\citeyear{Umurhan:2007dz}, \citeyear{Umurhan:2007hs}; hereafter URM07). The authors undertook the first weakly nonlinear analysis of the MRI in a thin-gap Taylor-Couette flow, and found that the marginal MRI system approaches saturation in a manner analogous to that of Rayleigh-B\'enard convection. Weakly nonlinear analysis was instrumental in our understanding of Rayleigh-B\'enard convection saturation (\citei{Newell:1969}), and the similarities between convection and the thin-gap MRI are the result of important shared symmetries between the systems. The success of URM07 in modeling the MRI system near threshold merits further consideration, but we are unaware of any other attempts to expand upon their theoretical framework. In this work we rigorously rederive the theory of URM07, and expand upon their findings. Our focus here is on fully characterizing the narrow gap MRI system, both for independent theoretical interest and to have a robust comparison point for extensions of this theory into more complicated geometries. In a companion paper we derive for the first time the weakly nonlinear theory of the standard and helical MRI in a wide gap Taylor-Couette flow \citep[][hereafter Paper II]{Clark:2016}. The thin- and wide-gap treatments complement one another theoretically, and both are important regimes for comparison with simulation.

This work examines Taylor-Couette flow in the thin-gap regime, an idealization in which the radial extent of the channel is very small compared to its distance from the center of rotation, i.e. $(r_2 - r_1) \ll \frac{1}{2} (r_1 + r_2)$ where $r_1$ and $r_2$ are the radii of the inner and outer flow boundaries, respectively. The thin-gap approximation eliminates curvature terms, so the domain geometry is Cartesian rather than cylindrical. The excluded curvature terms have an explicit dependence on $r$, so they make the problem more challenging both analytically and numerically. In particular, in the wide-gap geometry (i.e. true Taylor-Couette flow) the base angular velocity is a function of $r$, where in the thin-gap approximation the shear flow reduces to a linear profile.

We note several other important analytical studies of MRI saturation. \citeauthor{Knobloch:2005ba} (\citeyear{Knobloch:2005ba}) analyze the MRI in the strongly nonlinear regime, by following the already-developed MRI modes into asymptotic saturation. They find that this saturation proceeds via modification of the background shear. \citeauthor{Knobloch:2005ba} consider a thin-gap regime as well, and so their theory may be considered the strongly nonlinear analogue to the one developed here. \citei{Vasil:2015} examines the weakly nonlinear MRI in a thin-gap regime from a heuristic perspective, finding deep mathematical similarities between the MRI system and an elastodynamic instability. Several authors have investigated the behavior of the MRI when the boundary conditions are shear periodic, and so the MRI has no mechanism by which to modify the background shear flow profile. In this approximation linear MRI growth is dominated by channel modes, a type of MRI mode that, for periodic boundary conditions, are exact solutions of both the linear and nonlinear MRI equations (\citei{Goodman:1994ul}). In this regime the MRI saturates via parasitic instabilities, which feed off and destroy the primary MRI modes. Analytical investigation of this case reveals that MRI saturation can be caused by parasitic Kelvin-Helmholtz and tearing mode instabilities, depending on parameter regime (\citei{Pessah:2010ic}). The theory of MRI channel mode parasites is robust (see also \citei{Pessah:2009gm}, \citei{Latter:2010iz}, \citei{Rembiasz:2016}), but their importance may be overestimated by the local approximation \citei{Latter:2015}, and not germane to global analyses like the one presented here. \citei{Latter:2015} gives a  detailed analysis of the relation between local and global MRI modes.

@@

\begin{figure}[h!]
\centering
\includegraphics[trim=5cm 0cm 0cm 0cm, scale=.35]{setup_diagram.eps}
\caption{Schematic diagram of our set-up, an axisymmetric thin-gap Taylor-Couette flow. We investigate a 2D slice of the X-Z (radial-vertical) plane. Our domain is represented by the bolded black box, of width L. The radial dimension is solved with a basis of Chebyshev polynomials, and the vertical dimension is solved on a Fourier basis. }\label{fig:setup}
\end{figure}

@@

%See Figure \ref{figscalings}. 
Note that these are the same scalings as apply to Rayleigh-B\'enard convection and hydrodynamic Taylor-Couette flow. Our $x$ dimension, the direction of angular momentum transport, is analogous to the direction of temperature transport in the convection problem. In analogy to these problems, we posit slow variation in both $Z$ and $T$. Each operator is expanded to reflect these scalings -- for instance, $\partial_z$ becomes $\partial_z + \epsilon\partial_Z$. The fast and slow variables are treated as independent in the perturbation series analysis that follows.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../figures/thingap_saturation_mechanism_plots_velocity_slice60.png}
\caption{Top panel: Mean radial profile for $u_y^{saturated} - u_y^0$, the difference between the saturated azimuthal velocity profile and the initial azimuthal velocity profile (TC flow). Bottom panel: each term in the steady state force balance (Equation \ref{eqset2} with $\partial_t u_{y} = 0$). Saturated quantities are computed with $\alpha_{saturation} = \sqrt{b/c}$ and $\epsilon = 0.5$. The saturated state shows reduced shear in the bulk of the flow, outside of the boundary layers.} \label{fig:sat_comp_vel}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../figures/thingap_saturation_mechanism_plots_Bfield_slice60.png}
\caption{Top panel: Mean radial profile for $B_z^{saturated}$, the saturated vertical magnetic field (black line). $B_z^0 = 1$ is the constant background magnetic field (gray line). Bottom panel: each term in the steady state inductive balance ($\partial_x$ of Equation \ref{eqset4} with $\partial_t B_y = 0$). Saturated quantities are computed with $\alpha_{saturation} = \sqrt{b/c}$ and $\epsilon = 0.5$. The saturated field is pushed to the radial domain boundaries.}\label{fig:sat_comp_Bfield}
\end{figure}

@@

Figure~\ref{fig:sat_comp_Bfield} shows $B_z$ and the terms corresponding to steady state inductive balance ($\partial_x$ of Equation~\ref{eqset4} with $\partial_t B_{y} = 0$). Here, the instability acts to push magnetic field toward the boundaries in both the bulk and the boundary layers. Note also that the total magnetic energy in the $B_z$ component is significantly larger than the initial condition. \citet{Ebrahimi:2009ey} considered the saturation of a single, strongly super-critical MRI mode allowed to interact non-linearly only with itself and the mean. They considered two important cases, one in which the mean flow was forced to remain at its initial, quasi-Keplerian state for all time, and one in which the background flow was allowed to evolve. This is a crucial difference between the shearing box and our narrow-gap TC flow: perturbations in our simulation can adjust the background flow, whereas in a shearing box, the shear periodicity forbids perturbations from affecting the mean flow. In the case with a freely evolving background flow, \citet{Ebrahimi:2009ey} found a saturated state quite similar to ours: field pushed to the boundaries, and a reduction in shear in the bulk of the flow. Their flows have less pronounced boundary layers, likely because of their much larger $\Pm = 0.1 -1$.

In the high $\reye$ and  $\reym$  limit, \citet{Vasil:2015} derives an amplitude equation considerably different than the one found here. By averaging in the $z$ direction, he computes a mean-field equation with striking similarity to the buckling of an elastic beam under load. The most salient feature of his equation is its \emph{non-local} character. Unlike the present work, which focuses on Keplerian rotation profiles with $q = 3/2$ with a critical $B_0$, \citet{Vasil:2015} focuses on a fixed $B$ and a weakly destabilized shear profile. However, these differences are minor; the destabilizing parameter $\epsilon$ enters the analysis in the same quadratic proportion. Whether and how \citet{Vasil:2015}'s amplitude equation is equivalent to our own in the limit of dynamically important resistive and viscous effects is beyond the scope of this work.

@@

\section{Acknowledgements}
S.E.C. was supported by a National Science Foundation Graduate Research Fellowship under grant No. DGE-16-44869. J.S.O. acknowledges support from NASA grant 15-LWS15\_2-0063. The authors thank Mordecai Mac Low, Jeremy Goodman, John Krommes, Geoff Vasil, and Ellen Zweibel for useful discussion.

@@

@@

@@

@@

@@

@@

@@

>>>>

\title{The Weakly Nonlinear Magnetorotational Instability in a thin-gap Taylor Couette flow}
\author{Susan E. Clark\altaffilmark{1}}
\author{Jeffrey S. Oishi\altaffilmark{2,}\altaffilmark{3}}

@@

\begin{abstract}
The magnetorotational instability (MRI) is a fundamental process of accretion disk physics, but its saturation mechanism remains poorly understood despite considerable theoretical and computational effort. We present a multiple-scales analysis of the non-ideal MRI in the weakly nonlinear regime -- that is, when the the most unstable MRI mode has a growth rate asymptotically approaching zero from above. Here, we develop our theory in a thin-gap, Cartesian channel. Our results confirm Umurhan et al.'s findings that the saturation amplitude follows a Ginzburg-Landau equation. We extend these results by performing a detailed force balance for the saturated $u_y$ and $B_z$ fields, demonstrating that even when diffusive effects are important, the bulk flow saturates by a combination of reducing the background shear and rearranging and strengthening the background $B_z$ field. 
\end{abstract}

@@

For matter to accrete from a disk onto a central object, angular momentum must be transported radially outward in the disk. The transport mechanism is likely turbulent, as molecular viscosity alone cannot account for the needed angular momentum transfer, and likely magnetic, as this turbulence is excited even in hydrodynamically stable disks (\citei{Shakura:1973wg}).  Discovered by \citet{Chandrasekhar:1960wh} and \citet{Velikhov:1959} in global geometry, the MRI was subsequent rediscovered and applied to accretion disks by \citet{Balbus:1991vs}. Since then, the magnetorotational instability (MRI) remains the leading explanation for rapid angular momentum transport in astrophysical disks. The instability in its simplest geometry arises when a differentially rotating disk is threaded by a vertical magnetic field. The presence of the magnetic field linearly destabilizes the disk gas, driving turbulence and angular momentum transport \citep[e.g.][]{2011ApJ...738...84H,2014MNRAS.438.2513P,2013MNRAS.435.2281P}. The MRI likely plays a role in a diverse host of astrophysical systems, including protoplanetary disks \citep[e.g.]{2015ApJ...798...84B} and black hole accretion disks \citep[e.g.][]{2013ApJ...769..156S}, as well as stellar interiors \citep{2015ApJ...799...85W}. Despite its importance, many aspects of the MRI remain poorly understood. In particular, the nonlinear saturation mechanism for the MRI is an open question, and a formidable challenge. MRI saturation has been tackled almost exclusively with simulation, with a few notable exceptions detailed below. In this work we investigate the weakly nonlinear behavior of the MRI.

Weakly nonlinear analysis is a perturbative method used to examine the asymptotic behavior of a system near threshold -- that is, when the system is just barely unstable to its most unstable mode. The analytical technique follows the multiscale evolution of fluid variables in a perturbation expansion, allowing the controlled interaction of modes between orders in a perturbation series \citep{1978amms.book.....B}. Weakly nonlinear analysis can be a powerful technique for analytically examining systems which in their full generality exhibit such complicated nonlinear behavior that their study is relegated primarily to the simulation domain. The MRI is one such phenomenon: while there is a rich literature analytically examining the linear MRI, analytical treatments of the \textit{nonlinear} system are relatively few. The weakly nonlinear treatment of the MRI was pioneered by \citet{Knobloch:2005ba} and \citet[][hereafter URM07]{Umurhan:2007dz}. The latter authors undertook the first weakly nonlinear analysis of the MRI in a thin-gap Taylor Couette flow with strong dissipation (as is appropriate to liquid metal experiments), and found that the marginal MRI system approaches saturation in a manner analogous to that of Rayleigh-B\'enard convection. Weakly nonlinear analysis was instrumental in our understanding of Rayleigh-B\'enard convection saturation (\citei{Newell:1969}), and the similarities between convection and the thin-gap MRI are the result of important shared symmetries between the systems. The success of URM07 in modeling the MRI system near threshold merits further consideration, but we are unaware of any other attempts to expand upon their theoretical framework. In this work we rederive the theory of URM07, and expand upon their findings. Our focus here is on fully characterizing the narrow gap MRI system, both for independent theoretical interest and to have a robust comparison point for extensions of this theory into more complicated geometries. In a companion paper we derive for the first time the weakly nonlinear theory of the standard and helical MRI in a wide gap Taylor Couette flow \citep[][hereafter Paper II]{Clark:2016}. The thin- and wide-gap treatments complement one another theoretically, and both are important regimes for comparison with simulation.

This work examines Taylor Couette flow in the thin-gap regime, an idealization in which the radial extent of the channel is very small compared to its distance from the center of rotation, i.e. $(r_2 - r_1) \ll \frac{1}{2} (r_1 + r_2)$ where $r_1$ and $r_2$ are the radii of the inner and outer flow boundaries, respectively. The thin-gap approximation eliminates curvature terms, so the domain geometry is Cartesian rather than cylindrical. The excluded curvature terms have an explicit dependence on $r$, so they make the problem more challenging both analytically and numerically. In particular, in the wide-gap geometry (i.e. true Taylor Couette flow) the base angular velocity is a function of $r$, where in the thin-gap approximation the shear flow reduces to a linear profile.

We note several other important analytical studies of MRI saturation. \citeauthor{Knobloch:2005ba} (\citeyear{Knobloch:2005ba}) analyze the MRI in the strongly nonlinear regime, by following the already-developed MRI modes into asymptotic saturation. They consider a thin-gap regime as well, and so their theory may be considered the strongly nonlinear analogue to the one developed here. \citei{Vasil:2015} examines the weakly nonlinear MRI in a thin-gap regime in a minimal model, finding deep mathematical similarities between the MRI system and the elastodynamic instability of a buckling beam. We discuss his results and their relation to ours in section~\ref{sec:discussion}. Several authors have investigated the behavior of the MRI when the boundary conditions are shear periodic, and so the MRI has no mechanism by which to modify the background shear flow profile. In this approximation linear MRI growth is dominated by channel modes, a type of MRI mode that, for periodic boundary conditions, are exact solutions of both the linear and nonlinear MRI equations (\citei{Goodman:1994ul}). In this regime the MRI saturates via parasitic instabilities, which feed off and destroy the primary MRI modes. Analytical investigation of this case reveals that MRI saturation can be caused by parasitic Kelvin-Helmholtz and tearing mode instabilities, depending on parameter regime (\citei{Pessah:2010ic}). The theory of MRI channel mode parasites is robust (see also \citei{Pessah:2009gm}, \citei{Latter:2010iz}, \citei{Rembiasz:2016}), but their importance may be overestimated by the local approximation \citei{Latter:2015}, and not germane to global analyses like the one presented here. \citei{Latter:2015} gives a detailed analysis of the relation between local and global linear MRI modes.

We begin with an overview of our basic model equations for the thin gap MRI in section~\ref{sec:equations} and then describe our weakly non-linear analysis and give basic results in section~\ref{sec:wnl}. We then place our results in the ocntext of previous results from both analytic and computational studies in section~\ref{sec:discussion} and draw conclusions in section~\ref{sec:conclusion}.

@@

\begin{figure}[h!]
\centering
\includegraphics[trim=5cm 0cm 0cm 0cm, scale=.35]{setup_diagram.eps}
\caption{Schematic diagram of our set-up, an axisymmetric thin-gap Taylor Couette flow. We investigate a 2D slice of the X-Z (radial-vertical) plane. Our domain is represented by the bolded black box, of width L. The radial dimension is solved with a basis of Chebyshev polynomials, and the vertical dimension is solved on a Fourier basis. }\label{fig:setup}
\end{figure}

@@

%See Figure \ref{figscalings}. 
Note that these are the same scalings as apply to Rayleigh-B\'enard convection and hydrodynamic Taylor Couette flow. Our $x$ dimension, the direction of angular momentum transport, is analogous to the direction of temperature transport in the convection problem. In analogy to these problems, we posit slow variation in both $Z$ and $T$. Each operator is expanded to reflect these scalings -- for instance, $\partial_z$ becomes $\partial_z + \epsilon\partial_Z$. The fast and slow variables are treated as independent in the perturbation series analysis that follows.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../figures/thingap_saturation_mechanism_plots_velocity_slice60.png}
\caption{Top panel: Mean radial profile for $u_y^{saturated} - u_y^0$, the difference between the saturated azimuthal velocity profile and the initial azimuthal velocity profile (TC flow). Bottom panel: each term in the azimuthal velocity steady state force balance (Equation \ref{eqset2} with $\partial_t u_{y} = 0$).} \label{fig:sat_comp_vel}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../figures/thingap_saturation_mechanism_plots_Bfield_slice60.png}
\caption{.}\label{fig:sat_comp_Bfield}
\end{figure}

@@

Figure~\ref{fig:sat_comp_Bfield} shows $B_z$ and the terms corresponding to steady state inductive balance (Equation~\ref{eqset2} with $\partial_t B_{y} = 0$). Here, the instability acts to push magnetic field toward the boundaries in both the bulk and the boundary layers. Note also that the total magnetic energy in the $B_z$ component is significantly larger than the initial condition. \citet{Ebrahimi:2009ey} considered the saturation of a single, strongly super-critical MRI mode allowed to interact non-linearly only with itself and the mean. They considered two important cases, one in which the mean flow was forced to remain at its initial, quasi-Keplerian state for all time, and one in which the background flow was allowed to evolve. This is a crucial difference between the shearing box and our narrow-gap TC flow: perturbations in our simulation can adjust the background flow, whereas in a shearing box, the shear periodicity forbids perturbations from affecting the mean flow. In the case with a freely evolving background flow, \citet{Ebrahimi:2009ey} found a saturated state quite similar to ours: field pushed to the boundaries, and a reduction in shear in the bulk of the flow. Their flows have less pronounced boundary layers, likely because of their much larger $\Pm = 0.1 -1$.

In the high $\reye$ and  $\reym$  limit, \citet{Vasil:2015} derives an amplitude equation considerably different than the one found here. By averaging in the $z$ direction, he computes a mean-field equation with striking similarity to the buckling of an elastic beam under load. The most salient feature of his equation is its \emph{non-local} character. Unlike the present work, which focuses on Keplerian rotation profiles with $q = 3/2$ with a critical $B_0$, \citet{Vasil:2015} focuses on a fixed $B$ and a weakly destabilized shear profile. However, these differences are minor; the destabilizing parameter $\epsilon$ enters the analysis in the same quadratic proportion. Whether and how \citet{Vasil:2015}'s amplitude equation is equivalent to our own in the limit of dynamically important resistive and viscous effects is beyond the scope of this work. Nevertheless, he identifies the non-linear term responsible for saturation as consisting of flux and field transport and notes these are the only mechanisms that can produce saturation. Our results also demonstrate a combination of flux and field transport. This suggests that despite our formulation displaying different saturation dynamics (Ginzburg-Landau in our case; a network of coupled Duffing oscillators in his), there may indeed be an underlying unification.

@@

\section{Acknowledgments}
S.E.C. was supported by a National Science Foundation Graduate Research Fellowship under grant No. DGE-16-44869. J.S.O. acknowledges support from NASA grant 15-LWS15\_2-0063. The authors thank Mordecai Mac Low, Jeremy Goodman, John Krommes, Geoff Vasil, and Ellen Zweibel for useful discussion.

@@

\bibitem[Bai(2015)]{2015ApJ...798...84B} Bai, X.-N.\ 2015, \apj, 798, 84

@@

\bibitem[Bender \& Orszag(1978)]{1978amms.book.....B} Bender, C.~M., \& Orszag, S.~A.\ 1978, Advanced Mathematical Methods for Scientists and Engineers, New York: McGraw-Hill, 1978,

@@

\bibitem[Hawley et al.(2011)]{2011ApJ...738...84H} Hawley, J.~F., Guan, X., \& Krolik, J.~H.\ 2011, \apj, 738, 84

@@

\bibitem[Parkin(2014)]{2014MNRAS.438.2513P} Parkin, E.~R.\ 2014, \mnras, 438, 2513

\bibitem[Parkin \& Bicknell(2013)]{2013MNRAS.435.2281P} Parkin, E.~R., \& Bicknell, G.~V.\ 2013, \mnras, 435, 2281

@@

\bibitem[Schnittman et al.(2013)]{2013ApJ...769..156S} Schnittman, J.~D., Krolik, J.~H., \& Noble, S.~C.\ 2013, \apj, 769, 156

@@

\bibitem[Wheeler et al.(2015)]{2015ApJ...799...85W} Wheeler, J.~C., Kagan, D., \& Chatzopoulos, E.\ 2015, \apj, 799, 85

@@

%  LocalWords:  Magnetorotational Couette Oishi Lewiston Umurhan et
%  LocalWords:  magnetorotational al Ginzburg accrete Shakura wg wh
%  LocalWords:  hydrodynamically Velikhov Balbus protoplanetary ba ul
%  LocalWords:  perturbative analytical multiscale Orszag Knobloch ic
%  LocalWords:  URM enard Newell Vasil elastodynamic Pessah iz Alfv
%  LocalWords:  Rembiasz axisymmetric Chebyshev diffusivity zA xA aa
%  LocalWords:  incompressibility axisymmetrically nondimensionalize
%  LocalWords:  nondimensionalized nondimensional streamfunction ey
%  LocalWords:  Jacobian Colorbar azimuthal ansatz marginality Runge
%  LocalWords:  wavenumber pseudospectral Dedalus solvability Kutta
%  LocalWords:  axisymmetry advection Ebrahimi Keplerian timestep Im
%  LocalWords:  timesteps crit arctan colorbar hs DGE LWS Mordecai Xu
%  LocalWords:  Krommes Geoff Zweibel natexlab Bai Hawley Prager ApJ
%  LocalWords:  Schnack Guan Krolik Rebecca Julien Fromang Faure JFM
%  LocalWords:  MNRAS Gressel Parkin Bicknell Obergaulinger Cerd Dur
%  LocalWords:  uller Aloy Schnittman Sunyaev Regev Menou RSPSA Sov
%  LocalWords:  JETP Kagan Chatzopoulos
